{\bf \huge Wikiplia}:\\ The Free Programming Language\\ That Anyone Can Edit

### 2007-04-13 wikiplia/paper/wikiplia.tex
monoid joke, typo

Wikiplia is built upon a core calculus of structured data with
primitive revision control. Because we wish to support the freedom to
tinker, the structured data take the form of XML (the {\em extensible}
markup language; Figure~\ref{fig:xml}). Similar to the W3C's XML
Validation,\z\wcite{XML schema} we allow the quality of an XML
document to be assessed via a process called {\em evaluation}, whose
output (if any) is itself an XML document. Selected rules for XML
evaluation (the dynamic semantic markup) are given in
Figures~\ref{fig:xmleval}~and~\ref{fig:xmlrate}.\z\footnote{XML
documents can be self-correcting through the use of the {\sf handle}
primitive, which detects an invalid document and proceeds along an
alternative path. We omit the rules for this feature, which requires
propagating invalid document status throughout evaluation and thus
complicates the rules substantially.}

@@

The author\wcite{Author} doesn't think\wcite{Thought} much of
musicals,\z\wcite{Musical theatre} to be perfectly\wcite{Thomas
Aquinas} honest,\z\wcite{Honesty} so those are basically\wcite{BASIC}
a no-go. He also feels that the metric system\wcite{Metric system} but
paradoxically\wcite{Pardadox} also time zones\wcite{Time zone} are
pretty overrated. Ketchup\wcite{Ketchup} on eggs\wcite{Egg (food)} is
gross,\z\wcite{Gross} but not quite as gross as foie gras\wcite{Foie
gras}, which more or less has the word\wcite{Word} ``gross'' in its
name\wcite{Name} so duh.\z\wcite{Duh}

>>>>

Wikiplia is built upon a core calculus of structured data with
primitive revision control. Because we wish to support the freedom to
tinker, the structured data take the form of XML (the {\em extensible}
markup language; Figure~\ref{fig:xml}). Similar to the W3C's XML
Validation,\z\wcite{XML schema} we allow the quality of an XML
document to be assessed via a process called {\em evaluation}, whose
output (if any) is itself an XML document. Selected rules for XML
evaluation (the dynamic semantic markup) are given in
Figures~\ref{fig:xmleval}~and~\ref{fig:xmlrate}.\z\footnote{XML
documents can be self-correcting through the use of the {\sf handle}
primitive, which detects an invalid document and proceeds along an
alternative path. We omit the rules for this feature, which requires
propagating invalid document status throughout evaluation and thus
complicates the rules substantially.} Lists---delineated with the
$\tag{list}$ tag---play a central r\^ole because they are the free
moniod\wcite{Free monoid} on the set of XML documents, and we seek
to achieve freedom wherever possible.

@@

The author\wcite{Author} doesn't think\wcite{Thought} much of
musicals,\z\wcite{Musical theatre} to be perfectly\wcite{Thomas
Aquinas} honest,\z\wcite{Honesty} so those are basically\wcite{BASIC}
a no-go. He also feels that the metric system\wcite{Metric system} but
paradoxically\wcite{Pardadox} also time zones\wcite{Time zone} are
pretty overrated. Ketchup\wcite{Ketchup} on eggs\wcite{Egg (food)} is
gross,\z\wcite{Gross} but not quite as gross as foie
gras,\z\wcite{Foie gras} which more or less has the word\wcite{Word}
``gross'' in its name\wcite{Name} so duh.\z\wcite{Duh}
